---
title: "Accordion"
---

```{r}
library("htmltools")
library("bsplus")
```

The `bs_accordion()` family is an extension of the `bs_collapse()` family. An accordion is a set of collapsible panels constructed such that one panel, at most, is open at a time.

There are three functions in this family:

- `bs_accordion()`, used to establish the accordion framework
- `bs_append()`, used to add a panel (`title` and `content`) to the accordion
- `bs_set_opts()`, used to set options for the panels to follow

The `bs_accordion()` function takes a single argument, a unique `id` for the accordion frameowrk.

To add a panel to an accordion, use the `bs_append()` function. Its arguments are the `tag` of the accordion, the `title` of the panel, which will generally be text, and the `content` of the panel, which can be HTML.

The appearance of panels can be modified using the `bs_set_opts()` function. Its first argument is the accordion `tag`, its other arguments are `panel_type`, which controls the appearance of following panels, and `use_heading_link`, which, if `TRUE`, makes the entire headings of following panels of into links, rather than just the title. 

The default `panel_type` is `"default"`, the default for `use_heading_link` is `FALSE`.

All of these functions return an accordion tag; thus, you can build an accordion using a pipe.

```{r}
bs_accordion(id = "beatles") %>%
  bs_set_opts(panel_type = "success", use_heading_link = TRUE) %>%
  bs_append(title = "John Lennon", content = "Rhythm guitar, vocals") %>%
  bs_append(title = "Paul McCartney", content = "Bass guitar, vocals") %>%
  bs_append(title = "George Harrison", content = "Lead guitar, vocals") %>%
  bs_set_opts(panel_type = "info") %>%
  bs_append(title = "Ringo Starr", content = "Drums, vocals") 
```

The `panel_type` has to be one of the standard Bootstrap types: `c("default", "primary", "success", "info", "warning", "danger")`.

```{r}
bs_accordion(id = "bootstrap_types") %>%
  bs_set_opts(panel_type = "default") %>%
  bs_append(title = "Default", content = NULL) %>%
  bs_set_opts(panel_type = "primary") %>%
  bs_append(title = "Primary", content = NULL) %>%
  bs_set_opts(panel_type = "success") %>%
  bs_append(title = "Success", content = NULL) %>%
  bs_set_opts(panel_type = "info") %>%
  bs_append(title = "Info", content = NULL) %>%
  bs_set_opts(panel_type = "warning") %>%
  bs_append(title = "Warning", content = NULL) %>%
  bs_set_opts(panel_type = "danger") %>%
  bs_append(title = "Danger", content = NULL)
```

## Reference

For more information, please see the [Bootstrap JavaScript page](http://getbootstrap.com/docs/3.3/javascript/#collapse-example-accordion).

