---
title: "Accordion Sidebar"
author: "Ian Lyttle"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
---

```{r}
library("htmltools")
library("bsplus")
```

An accordion-sidebar can be useful to provide another dimension for your **shiny** apps. For example, you can use **shiny** `navbarPage()` for major groupings, then `bs_accordion_sidebar()` panels for minor groupings within each major grouping.

There are three functions in this family:

- `bs_accordion_sidebar()`, used to establish the accordion-sidebar framework
- `bs_append()`, used to add a side panel (`title_side` and `content_side`) and a main panel (`content_main`) to the accordion sidebar 
- `bs_set_opts()`, used to set options for the panel-sets to follow

The `bs_accordion_sidebar()` function is used to instantiate the accordion sidebar. Its argument, are a unique `id`, Boostrap column-specifications `spec_side` and `spec_main`, and an indication of the relative `position` of the side panel to the main panel.

To add a panel set to an accordion sidebar, use the `bs_append()` function. Its arguments are the `tag` of the accordion sidebar, the `title_side` of the side panel, which will generally be text, the `content_side` of the side panel, which can be HTML (might be **shiny** inputs), and the `content_main` of the main panel, which can also be HTML (might be **shiny** outputs).

The appearance of panel sets can be modified using the `bs_set_opts()` function. Its first argument is the accordion sidebar `tag`, its other arguments are `panel_type_active` and `panel_type_inactive`, which control the appearance of following panels, and `use_main_enclosure`, which, if `TRUE`, encloses the content of the main panel in an HTML `<panel/>`. 

The default `panel_type_active` is `"success"`, for `panel_type_inactive` it is `"primary"`, the default for `use_main_enclosure` is `TRUE`.

All of these functions return an accordion tag; thus, you can build an accordion sidebar using a pipe.

```{r}
bs_accordion_sidebar(id = "beatles") %>%
  bs_append(
    title_side = "John Lennon", 
    content_side = "Rhythm guitar, vocals",
    content_main = "Dear Prudence"
  ) %>%
  bs_append(
    title_side = "Paul McCartney", 
    content_side = "Bass guitar, vocals",
    content_main = "Blackbird"
  ) %>%
  bs_append(
    title_side = "George Harrison", 
    content_side = "Lead guitar, vocals",
    content_main = "While My Guitar Gently Weeps"
  ) %>%
  bs_append(
    title_side = "Ringo Starr", 
    content_side = "Drums, vocals",
    content_main = "Don't Pass Me By"
  ) 
```

As you can see, the sidebar acts like a `bs_accordion()`, but there are a couple of important differences. First, a sidebar panel's class changes according to its being open or not. Second, the state (show-hide) of each component's main panel is determined by the state of its side panel.

When showing him a preview of this work, Carson Sievert asked a crazy question, "can you nest those things?" Well, apparently you can. 

Note that the outer accordion-sidebar has `use_main_enclosure` set to `FALSE`, while each inner accordion-sidebar has it set to `TRUE`.

```{r}
bs_accordion_sidebar(id = "the_beatles") %>%
  bs_set_opts(use_main_enclosure = FALSE) %>%
  bs_append(
    title_side = "John Lennon", 
    content_side = NULL,
    content_main = 
      bs_accordion_sidebar(id = "john") %>%
      bs_append(
        title_side = "Beatles",
        content_side = "1960-1969",
        content_main = "Help!"
      ) %>%
      bs_append(
        title_side = "Solo",
        content_side = "1968-1980",
        content_main = "Love"
      )
  ) %>%
  bs_append(
    title_side = "Paul McCartney", 
    content_side = NULL,
    content_main =
      bs_accordion_sidebar(id = "paul") %>%
      bs_append(
        title_side = "Beatles",
        content_side = "1960-1970",
        content_main = "Yesterday"
      ) %>%
      bs_append(
        title_side = "Solo",
        content_side = "1970-",
        content_main = "Maybe I'm Amazed"
      )
  ) %>%
  bs_append(
    title_side = "George Harrison", 
    content_side = NULL,
    content_main = 
      bs_accordion_sidebar(id = "george") %>%
      bs_append(
        title_side = "Beatles",
        content_side = "1960-1970",
        content_main = "Here Comes the Sun"
      ) %>%
      bs_append(
        title_side = "Solo",
        content_side = "1968-2001",
        content_main = "My Sweet Lord"
      )
  ) %>%
  bs_append(
    title_side = "Ringo Starr", 
    content_side = NULL,
    content_main = 
      bs_accordion_sidebar(id = "ringo") %>%
      bs_append(
        title_side = "Beatles",
        content_side = "1962-1970",
        content_main = "Octopus' Garden"
      ) %>%
      bs_append(
        title_side = "Solo",
        content_side = "1970-",
        content_main = "Photograph"
      )
  ) 
```

To use an accordion sidebar, you will need to insert some JavaScript code into your page using the `use_bs_accordion_sidebar()` function. You will have to do this only once per page; I have found that it works best to include after all of the accordion-sidebars are defined, perhaps as one of the last elements in a **shiny** UI.

```{r}
use_bs_accordion_sidebar()
```
