---
title: "Carousel"
---

```{r}
library("htmltools")
library("bsplus")
```

A carousel can be useful to cycle through slides with related content. There like the accordion, there are two main functions:

- `bs_carousel()`, used to establish the carousel framework, with arguments `id`, `use_indicators`, for the "dots" indicating the slide, and `use_controls`, for the directional controls at either side. 
- `bs_append()`, used to add a slide containing `content`, which is HTML, and an optional `caption`.

The `content` and `caption` arguments can be composed using the helper functions `bs_carousel_image()`, which returs a centered-image tag, and `bs_carousel_caption()` with text arguments `title` and `body`.

```{r}
bs_carousel(id = "the_beatles", use_indicators = TRUE) %>%
  bs_append(
    content = bs_carousel_image(src = "img/john.jpg", alt = "John Lennon"),
    caption = bs_carousel_caption("John Lennon", "Rhythm guitar, vocals")
  ) %>%
  bs_append(
    content = bs_carousel_image(src = "img/paul.jpg", alt = "Paul McCartney"),
    caption = bs_carousel_caption("Paul McCartney", "Bass guitar, vocals")
  ) %>%
  bs_append(
    content = bs_carousel_image(src = "img/george.jpg", alt = "George Harrison"),
    caption = bs_carousel_caption("George Harrison", "Lead guitar, vocals")
  ) %>%
  bs_append(
    content = bs_carousel_image(src = "img/ringo.jpg", alt = "Ringo Starr"),
    caption = bs_carousel_caption("Ringo Starr", "Drums, vocals")
  ) 
```

Here's another rendering of the carousel, this time:

- without indicators
- without captions
- the slides do not auto-advance (using `bs_set_data()` to set [Bootstrap options](http://getbootstrap.com/docs/3.3/javascript/#carousel-options))

```{r}
bs_carousel(id = "with_the_beatles") %>%
  bs_set_data(interval = FALSE) %>%
  bs_append(content = bs_carousel_image(src = "img/john.jpg", alt = "John Lennon")) %>%
  bs_append(content = bs_carousel_image(src = "img/paul.jpg", alt = "Paul McCartney")) %>%
  bs_append(content = bs_carousel_image(src = "img/george.jpg", alt = "George Harrison")) %>%
  bs_append(content = bs_carousel_image(src = "img/ringo.jpg", alt = "Ringo Starr")) 
```

## Reference

For more information, please see the [Bootstrap JavaScript page](http://getbootstrap.com/docs/3.3/javascript/#carousel).
