---
title: "Collapse"
author: "Ian Lyttle"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
---

```{r}
library("htmltools")
library("bsplus")
```

The `bs_collapse()` family of functions may not be the most useful, but it gives us a place to start. 

The first step is to create (and publish to the page) a collapsible element, using the `bs_collapse()` function, supplying a unique `id` and some HTML `content`.

```{r bs_collapse}
bs_collapse(
  id = "yeah", 
  content = tags$div(class = "well", "Yeah Yeah Yeah")
)
```

Next, attach the `id` of the collapsible element to a button or link tag, using the `bs_attach_collapse()` function. This returns a modified copy of the tag sent to it.

```{r bs_attach_collapse}
bs_button("She Loves You", button_type = "primary") %>%
  bs_attach_collapse("yeah")
```

You can attach the `id` of a collapsible element to as many buttons or links as you like:

```{r new_button}
bs_button("Sie Liebt Dich", button_type = "primary")  %>%
  bs_attach_collapse("yeah")
```

## Reference

For more information, please see the [Bootstrap JavaScript page](http://getbootstrap.com/docs/3.3/javascript/#collapse).
