---
title: "Modals"
author: "Ian Lyttle"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
---

```{r}
library("htmltools")
library("bsplus")
```

Modal windows are a great way to deliver help-documentation, although they certainly have other uses. The first step is to define a modal widow, giving it an `id`.

```{r}
bs_modal(id = "modal", title = "I'm a modal", body = "Yes, I am.")
```

To allow activation of the modal window, attach its `id` to a button (or link).

```{r}
tags$button(type = "button", class = "btn btn-default", "Click for modal") %>%
  bs_attach_modal(id_modal = "modal")
```

The verb *attach* implies that you can attach an `id` to as many link tags you like. Thus: 

```{r}
tags$button(type = "button", class = "btn btn-default", "New button, same modal") %>%
  bs_attach_modal(id_modal = "modal")
```

Let's look at a more-involved example using all of the arguments for `bs_modal()`. 

In the example above, `body` is text; usually, you will want the `body` to HTML. One way to compose the HTML for the body is to write it as a Markdown file, then use the helper function `shiny::includeMarkdown()` to render it into into HTML. 

The default `footer` is simply a "Close" button, which is made using the helper function `bs_modal_closebutton()`. You can compose your own footer, using this function to customize your close-button.

Finally, the `size` can be `"small"`, `"medium"`, or `"large"` - the defualt is `"medium"`.

```{r}
bs_modal(
  id = "modal_markdown", 
  title = "Using Markdown",
  body = includeMarkdown(system.file("markdown", "modal.md", package = "bsplus")),
  footer = tags$span(
    tags$span(class = "well", "Hello!"),
    bs_modal_closebutton("Goodbye!")
  ),
  size = "large"
)

tags$button(type = "button", class = "btn btn-default", "Large modal") %>%
  bs_attach_modal(id_modal = "modal_markdown")
```

## Reference

For more information, please see the [Bootstrap JavaScript page](http://getbootstrap.com/javascript/#modals).
