---
title: "Overview"
author: "Ian Lyttle"
date: "`r Sys.Date()`"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The goal of **bsplus** is to provide access to some useful components not already offered in Shiny:

- [collapse](http://getbootstrap.com/javascript/#collapse)

- [accordion](http://getbootstrap.com/javascript/#collapse-example-accordion)

- [modal](http://getbootstrap.com/javascript/#modals)

- [tooltip](http://getbootstrap.com/javascript/#tooltips)

- [popover](http://getbootstrap.com/javascript/#popovers)

- [carousel](http://getbootstrap.com/javascript/#carousel)

We also propose a compound component:

- accordion_sidebar

```{r echo=FALSE}
library("htmltools")
library("shiny")
library("bsplus")
library("knitr")
```

## Collapse

A collapsible element is attached to a button or link, which is used to show (or hide) the element.

```{r collapse}
tags$button(class = "btn btn-primary", "Click me") %>%
  bs_attach_collapse(id_collapse = "ex_collapse")

bs_collapse(id = "ex_collapse", content = tags$p("Hi there")) 
```

To see more of the collapse function-family, please see its vignette.

## Accordion

```{r accordion}
bs_accordion(id = "meet_the_beatles") %>%
  bs_append(title = "John", content = "Rhythm guitar, vocals") %>%
  bs_append(title = "Paul", content = "Bass guitar, vocals") %>%
  bs_append(title = "George", content = "Lead guitar, vocals") %>%
  bs_append(title = "Ringo", content = "Drums, vocals")
```

To see more of the accordion function-family, including how to make the entire banner "clickable" and how to change the class of the panels, please see its vignette.

## Accordion sidebar

An accordion-sidebar can be useful to provide another dimension for your **shiny** apps. You can place your inputs into a sidebar, and your outputs into the main panel. 

```{r accordion_sidebar}
bs_accordion_sidebar(id = "beatles") %>%
  bs_append(
    title_side = "John Lennon", 
    content_side = "Rhythm guitar, vocals",
    content_main = "Dear Prudence"
  ) %>%
  bs_append(
    title_side = "Paul McCartney", 
    content_side = "Bass guitar, vocals",
    content_main = "Blackbird"
  ) %>%
  bs_append(
    title_side = "George Harrison", 
    content_side = "Lead guitar, vocals",
    content_main = "While My Guitar Gently Weeps"
  ) %>%
  bs_append(
    title_side = "Ringo Starr", 
    content_side = "Drums, vocals",
    content_main = "Don't Pass Me By"
  ) 

use_bs_accordion_sidebar()
```

It is important call the `use_bs_accordion_sidebar()` function.

## Modal

Need to adjust the pkgdown css to keep the links from interfering with the 

```{r modal}
bs_modal(
  id = "modal_markdown", 
  title = "Using Markdown",
  body = render_html_fragment(
    system.file("markdown", "modal.md", package = "bsplus"),
    quiet = TRUE
  )
)

tags$button(type = "button", class = "btn btn-primary", "Click for modal") %>%
  bs_attach_modal(id_modal = "modal_markdown")

tags$button(
  type = "button", 
  class = "btn btn-primary", 
  "Different button, same modal"
) %>%
  bs_attach_modal(id_modal = "modal_markdown")
```

## Tooltip

```{r tooltip}
tags$button(type = "button", class = "btn btn-default", "John Lennon") %>%
  bs_embed_tooltip(title = "Rhythm Guitar, vocals")

use_bs_tooltip()
```

Make sure that you call `use_bs_tooltip()`.

## Popover

```{r popover}
tags$button(type = "button", class = "btn btn-primary","John Lennon") %>%
  bs_embed_popover(
    title = "More information",
    content = "Although he wrote \"I Am the Walrus\", he later insisted that the Walrus was Paul."
  )

use_bs_popover()
```

Make sure that you call `use_bs_popover()`.

## Carousel

```{r}
bs_carousel(id = "the_beatles", use_indicators = TRUE) %>%
  bs_append(
    content = bs_carousel_image(src = image_uri("img/john.jpg"), alt = "John Lennon"),
    caption = bs_carousel_caption("John Lennon", "Rhythm guitar, vocals")
  ) %>%
  bs_append(
    content = bs_carousel_image(src = image_uri("img/paul.jpg"), alt = "Paul McCartney"),
    caption = bs_carousel_caption("Paul McCartney", "Bass guitar, vocals")
  ) %>%
  bs_append(
    content = bs_carousel_image(src = image_uri("img/george.jpg"), alt = "George Harrison"),
    caption = bs_carousel_caption("George Harrison", "Lead guitar, vocals")
  ) %>%
  bs_append(
    content = bs_carousel_image(src = image_uri("img/ringo.jpg"), alt = "Ringo Starr"),
    caption = bs_carousel_caption("Ringo Starr", "Drums, vocals")
  ) 
```






