---
title: "Tooltips and Popovers"
---

```{r}
library("htmltools")
library("bsplus")
```

Tooltips and popovers are used to add additional content, like short notes. They can be useful for short help-documentation. A tooltip is used to embed a short note into a tag; by default they are activated by hovering over the tag. A popover is used to embed a longer note into a tag; by default they are activated by clicking on the tag. A tooltip has only a text `title`; a popover has a `title`, which is generally text, and `content`, which can be HTML.

```{r}
bs_button("Hover for tooltip") %>%
  bs_embed_tooltip(title = "I'm a tooltip")
```

```{r}
bs_button("Click for popover") %>%
  bs_embed_popover(title = "I'm a popover", content = "Really!")
```

Both of these functions have an additional argument, `placement`, which defaults to `"top"`, following the Bootstrap default. The possible values are `c("top", "bottom", "left", "right", "auto")`.

```{r}
bs_button("Another tooltip") %>%
  bs_embed_tooltip(title = "I'm on the right", placement = "right")
```

Tooltips and popovers are not activted by default in Bootstrap. For either of them to work properly, you will have to activate them on your page, using the `use_bs_tooltip()` or `use_bs_popover()` functions. For each page you write, you will need to call each function once, at most. 

```{r}
use_bs_tooltip()
use_bs_popover()
```

## Reference

For more information, please see the Bootstrap JavaScript page on [tooltips](http://getbootstrap.com/docs/3.3/javascript/#tooltips) or [popovers](http://getbootstrap.com/docs/3.3/javascript/#popovers).

