---
title: "Collapse"
---

```{r}
library("htmltools")
library("bsplus")
```

The collapse family of functions may not be the most useful, but it gives us a place to start. 


## Example

First, let's build the stuff we will put into the collapse elements:

```{r button}
button <- tags$button("She Loves You")
hidden <- tags$div(class = "well", "Yeah Yeah Yeah")
```

Now let's create our collapsible content. The first step is to create the div using the `collapse()` function, supplying a unique id and the content to include.

```{r collapse}
collapse(id = "id_yeah", content = hidden)
```

Next we attach the id of our collapsible div to our button using the `attach_collapse()` function, which returns a modified copy of the button or link sent to it.

```{r attach_collapse}
button %>%
  attach_collapse(id_collapse = "id_yeah")
```

You are able to attach a collapsible div to a button or to a link. In fact, you are able to attach a collapsible div to as many buttons or links as you like:

```{r new_button}
tags$button("Sie Liebt Dich") %>%
  attach_collapse("id_yeah")
```
